---
title: "FirstMarkdown"
author: "Arnav Bajwa"
date: "September 23, 2018"
output: html_document
---
**Bold**-bold with double asterisks  
_Italics_- Italics with underscore  
`r`- Code with backticks

# Title  
## Main Section  
### Sub Section 
#### Sub-Sub Section

- Item 1 
- Item 2 
- Item 3 

1. Item 1 
2. Item 2 
3. Item 3 

1. Item 1 
1. Item 2 
1. Item 3 

<https://www.google.com>

[](../Canada.png)

$E = mc^2$

```{r load_data}
```{r ggplot_lifeExp}
library(ggplot2)

gapminder <- read.table("../Data/gapminder.txt",header=T)
Canada<-gapminder[gapminder$country=="Canada",]

ggplot(data = Canada, aes(x=year,y = lifeExp, by = country, color=continent)) + geom_line()


```{r working_of_knitr}
### Run this code in R to see graphic of how
### your document gets rendered
par(mar=rep(0, 4), bty="n", cex=1.5)
plot(0, 0, type="n", xlab="", ylab="", xaxt="n", yaxt="n",
     xlim=c(0, 100), ylim=c(0, 100))
xw <- 10
yh <- 35
xm <- 12
ym <- 50
rect(xm-xw/2, ym-yh/2, xm+xw/2, ym+yh/2, lwd=2)
text(xm, ym, ".Rmd")

xm <- 50
ym <- 80
rect(xm-xw/2, ym-yh/2, xm+xw/2, ym+yh/2, lwd=2)
text(xm, ym, ".md")
xm <- 50; ym <- 25
for(i in c(2, 0, -2))
    rect(xm-xw/2+i, ym-yh/2+i, xm+xw/2+i, ym+yh/2+i, lwd=2,
         border="black", col="white")
text(xm-2, ym-2, "figs/")

xm <- 100-12
ym <- 50
rect(xm-xw/2, ym-yh/2, xm+xw/2, ym+yh/2, lwd=2)
text(xm, ym, ".html")

arrows(22, 50, 38, 50, lwd=2, col="slateblue", len=0.1)
text((22+38)/2, 60, "knitr", col="darkslateblue", cex=1.3)

arrows(62, 50, 78, 50, lwd=2, col="slateblue", len=0.1)
text((62+78)/2, 60, "pandoc", col="darkslateblue", cex=1.3)
